The SMT Competition 2015--2018

### 2019-08-27 2018/report/SMT-COMP.tex
log -> ln

The competition-wide ranking for the \maintrack was retained and
refined after~2014.  Sequential and parallel performance are reported
separately.  Let $N_i$ be the total number of benchmarks in
division~$i$ that were used in the competition (and not removed
because of disagreements), and let $\langle e_i, n_i, w_i, c_i\rangle$
be a solver's raw score for this division.
%
In 2015 and~2016, the \emph{competition-wide raw score} for a solver
was defined as
%
$$\sum_i (e_i == 0 \,?\, (n_i/N_i)^2 : -e_i) \log N_i$$
%
where the sum is over all competitive divisions into which the solver
was entered.
%
In 2017, the (per-division) penalty for erroneous results was changed
from the number of errors to a fixed constant, since the division
weight~$\log N_i$ already takes the number of benchmarks in the
division into account, and multiplying it by the number of errors
overemphasizes large divisions.  In 2017 and 2018, the
\emph{competition-wide raw score} for a solver was thus defined as
%
$$\sum_i (e_i == 0 \,?\, (n_i/N_i)^2 : -4) \log_e N_i$$
%
The value of this constant was chosen to balance the strong interest
in correct solvers against the risk of stifling innovation.  In the
division rankings (Section~\ref{sec:scoring-division-rankings}), an
incorrect response causes a solver to be ranked below all correct
solvers for that division.  But the competition's \maintrack consists
of many independent divisions; a solver bug that affects one division
need not manifest itself in other divisions.  With the current value,
entering a (possibly buggy) solver that can solve all benchmarks into
a division has a positive expected score if the probability that a
soundness bug in the solver will be triggered is below~$20\,\%$.

>>>>

The competition-wide ranking for the \maintrack was retained and
refined after~2014.  Sequential and parallel performance are reported
separately.  Let $N_i$ be the total number of benchmarks in
division~$i$ that were used in the competition (and not removed
because of disagreements), and let $\langle e_i, n_i, w_i, c_i\rangle$
be a solver's raw score for this division.
%
In 2015 and~2016, the \emph{competition-wide raw score} for a solver
was defined as
%
$$\sum_i (e_i == 0 \,?\, (n_i/N_i)^2 : -e_i) \ln N_i$$
%
where the sum is over all competitive divisions into which the solver
was entered.
%
In 2017, the (per-division) penalty for erroneous results was changed
from the number of errors to a fixed constant, since the division
weight~$\ln N_i$ already takes the number of benchmarks in the
division into account, and multiplying it by the number of errors
overemphasizes large divisions.  In 2017 and 2018, the
\emph{competition-wide raw score} for a solver was thus defined as
%
$$\sum_i (e_i == 0 \,?\, (n_i/N_i)^2 : -4) \ln N_i$$
%
The value of this constant was chosen to balance the strong interest
in correct solvers against the risk of stifling innovation.  In the
division rankings (Section~\ref{sec:scoring-division-rankings}), an
incorrect response causes a solver to be ranked below all correct
solvers for that division.  But the competition's \maintrack consists
of many independent divisions; a solver bug that affects one division
need not manifest itself in other divisions.  With the current value,
entering a (possibly buggy) solver that can solve all benchmarks into
a division has a positive expected score if the probability that a
soundness bug in the solver will be triggered is below~$20\,\%$.
